### 2024-01-21 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Update paper Quarto file with outlines

---
title: "paper"
author: "Chay Park"
date: 
format: pdf
editor: visual
---

# Abstract

# Introduction

# Data

# References

Gelfand, Sharla. 2020. *Opendatatoronto : Access the City of Toronto Open Data Portal*

R Core Team. 2020. *R: A Language and Environment for Statistical Computing.* Vienna, Austria: R Foundation for Statistical Computing. https://www.R-project.org/.

Toronto Police Services. 2023. *TPS Police Annual Statistical Report - Victims of Crimes*

Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019. "Welcome to the tidyverse." *Journal of Open Source Software* 4 (43): 1686. https://doi.org/10.21105/joss.01686.

\
Wickham, Hadley, Romain François, Lionel Henry, and Kirill Müller. 2021. *Dplyr: A Grammar of Data Manipulation.*https://CRAN.R-project.org/package=dplyr.

Xie, Yihui. 2014. "Knitr: A Comprehensive Tool for Reproducible Research in R." *In Implementing Reproducible Computational Research*, edited by Victoria Stodden, Friedrich Leisch, and Roger D. Peng. Chapman; Hall/CRC. http://www.crcpress.com/product/isbn/9781466561595.

### 2024-01-22 Toronto_Victims_of_Crimes/scripts/01-download_data.R
Save in scripts folder

@@ -1,0 +1,36 @@
+#### Preamble ####
+# Purpose: Downloads and saves the data from opendatatoronto
+# Author: Chay Park
+# Date: 20 January 2024
+# Contact: chay.park@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: download the actual data in a reproducible way using opendatatoronto. 
+# Save the data: "inputs/data/unedited_data.csv"
+
+#### Save data ####
+
+# Install the package
+install.packages("opendatatoronto")
+
+# See a list of available packages
+library(opendatatoronto)
+packages <- list_packages(limit = 10)
+packages
+
+# Search packages by title
+victims_packages <- search_packages("victims")
+
+victims_packages
+
+# List resources from package
+victims_resources <- victims_packages %>%
+  list_package_resources()
+
+victims_resources
+
+# Download the resources
+victims_statistics <- victims_resources %>%
+  head(1) %>%
+  get_resource()
+
+victims_statistics

### 2024-01-22 Toronto_Victims_of_Crimes/inputs/data/01-download_data.R
Delete the file in wrong folder

@@ -1,36 +1,0 @@
-#### Preamble ####
-# Purpose: Downloads and saves the data from opendatatoronto
-# Author: Chay Park
-# Date: 20 January 2024
-# Contact: chay.park@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: download the actual data in a reproducible way using opendatatoronto. 
-# Save the data: "inputs/data/unedited_data.csv"
-
-#### Save data ####
-
-# Install the package
-install.packages("opendatatoronto")
-
-# See a list of available packages
-library(opendatatoronto)
-packages <- list_packages(limit = 10)
-packages
-
-# Search packages by title
-victims_packages <- search_packages("victims")
-
-victims_packages
-
-# List resources from package
-victims_resources <- victims_packages %>%
-  list_package_resources()
-
-victims_resources
-
-# Download the resources
-victims_statistics <- victims_resources %>%
-  head(1) %>%
-  get_resource()
-
-victims_statistics

### 2024-01-22 Toronto_Victims_of_Crimes/scripts/01-download_data.R
Add the code to download the actual data in csv file

@@ -11,9 +11,16 @@
 
 # Install the package
 install.packages("opendatatoronto")
+install.packages("knitr")
+install.packages("lubridate")
+install.packages("tidyverse")
 
 # See a list of available packages
+library(knitr)
+library(lubridate)
 library(opendatatoronto)
+library(tidyverse)
+
 packages <- list_packages(limit = 10)
 packages
 
@@ -34,3 +41,10 @@ victims_statistics <- victims_resources %>%
   get_resource()
 
 victims_statistics
+
+# Write CSV file
+write_csv(
+  x = victims_resources,
+  file = "unedited_data.csv"
+)
+head(victims_statistics)

### 2024-01-22 Toronto_Victims_of_Crimes/scripts/01-download_data.R
Update the file directory to save the unedited data in csv file.

@@ -45,6 +45,6 @@ victims_statistics
 # Write CSV file
 write_csv(
   x = victims_resources,
-  file = "unedited_data.csv"
+  file = "Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv"
 )
 head(victims_statistics)

### 2024-01-22 Toronto_Victims_of_Crimes/scripts/01-download_data.R
Data table was incorrect, updated data to write CSV

@@ -44,7 +44,7 @@ victims_statistics
 
 # Write CSV file
 write_csv(
-  x = victims_resources,
+  x = victims_statistics,
   file = "Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv"
 )
 head(victims_statistics)

### 2024-01-22 Toronto_Victims_of_Crimes/scripts/02-data_cleaning.R
Update data cleaning file

@@ -1,0 +1,14 @@
+library(dplyr)
+library(knitr)
+library(lubridate)
+library(tidyverse)
+
+# Check and set the working directory if needed
+# setwd("project/Toronto_Victims_of_Crimes")
+
+# Read the CSV file
+crime_data <- read.csv("Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv")
+
+# Filter out unknown values for SEX and rows with 'other' values for SUBTYPE
+filtered_data <- crime_data %>%
+  filter(SEX %in% c("M", "F") & SUBTYPE %in% c("Robbery", "Sexual violation", "Assault"))

### 2024-01-22 Toronto_Victims_of_Crimes/scripts/02-data_cleaning.R
Update 02-data_cleaning file

@@ -3,12 +3,12 @@ library(knitr)
 library(lubridate)
 library(tidyverse)
 
-# Check and set the working directory if needed
-# setwd("project/Toronto_Victims_of_Crimes")
-
 # Read the CSV file
 crime_data <- read.csv("Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv")
 
 # Filter out unknown values for SEX and rows with 'other' values for SUBTYPE
 filtered_data <- crime_data %>%
-  filter(SEX %in% c("M", "F") & SUBTYPE %in% c("Robbery", "Sexual violation", "Assault"))
+  filter(SEX %in% c("M", "F") & AGE_GROUP != "Unknown" & SUBTYPE != "Other")
+
+head(filtered_data)
+

### 2024-01-22 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Update paper file 1/3 much

@@
 author: "Chay Park"
-date: 
+date: 22 January 2024
 format: pdf
@@
 
+### top-level finding, what is the one thing that we learn about the world because of this paper?
+
+Often we see crimes on the global news and majority is happening in the States.
+Canada is known to be relatively safe country around the world.
+Toronto is one of the biggest city in Canada and thus the most populated.
+By investigating the dataset from Toronto Police Services, this report demonstrate the top four crimes reported over the year from 2014 to 2022.
+
 # Introduction
+
+Why I deal with this data?
+How would you answer to the following question?
+Between male and female, which sex would count more as a victim of sexual violation, which age group is proned to be the victims of assault?
+We could assume that it is mostly young age group or female are prone to be the victims of crimes.
+Often people judge and assume which leads to Misperception of victims of crimes.
+
+This paper use R to analyze a dataset from opendatatoronto.
+This dataset includes all identified victims of crimes against the person, including, but not limited to, those that may have been deemed unfounded after investigation, those that may have occurred outside the City of Toronto limits, or have no verified location.
+The paper extract age group, count, sex, subtype of crimes, report year.
+
+Visualize trend among the sex, age group per crime. The tendency of male not reporting might skew the result.
 
@@
 
+The data is
+
+```{r}
+# Install required packages
+
+install.packages("dplyr")
+install.packages("knitr")
+install.packages("lubridate")
+install.packages("tidyverse")
+```
+
+```{r}
+# Load required libraries
+library(dplyr)
+library(knitr)
+library(lubridate)
+library(tidyverse)
+
+# Input filtered_data from the R script (saved as 02-data-cleaning) that was separately saved to clean the data set
+
+# Create separate tables for each crime subtype
+table_robbery <- filtered_data %>%
+  filter(SUBTYPE == "Robbery") %>%
+  group_by(REPORT_YEAR, SEX) %>%
+  summarise(Victims_Count = sum(COUNT_)) %>%
+  spread(key = SEX, value = Victims_Count)
+
+table_sexual_violation <- filtered_data %>%
+  filter(SUBTYPE == "Sexual Violation") %>%
+  group_by(REPORT_YEAR, SEX) %>%
+  summarise(Victims_Count = sum(COUNT_)) %>%
+  spread(key = SEX, value = Victims_Count)
+
+table_assault <- filtered_data %>%
+  filter(SUBTYPE == "Assault") %>%
+  group_by(REPORT_YEAR, SEX) %>%
+  summarise(Victims_Count = sum(COUNT_)) %>%
+  spread(key = SEX, value = Victims_Count)
+
+# Print the tables using knitr
+kable(table_robbery, format = "markdown", caption = "Table for Robbery")
+kable(table_sexual_violation, format = "markdown", caption = "Table for Sexual Violation")
+kable(table_assault, format = "markdown", caption = "Table for Assault")
+```
+
+```{r}
+# Plotting using ggplot2
+# Define a function to create a count chart
+plot_count_chart <- function(data, crime_type) {
+  ggplot(data, aes(x = REPORT_YEAR, y = M, color = "Male")) +
+    geom_point() +
+    geom_line() +
+    geom_point(aes(y = F, color = "Female")) +
+    labs(title = paste("Count Chart for", crime_type),
+         x = "Year Reported",
+         y = "Count",
+         color = "Sex") +
+    scale_color_manual(values = c("Male" = "purple", "Female" = "blue"))
+}
+
+# Create count charts
+plot_robbery <- plot_count_chart(table_robbery, "Robbery")
+plot_sexual_violation <- plot_count_chart(table_sexual_violation, "Sexual Violation")
+plot_assault <- plot_count_chart(table_assault, "Assault")
+
+# Print the plots
+print(plot_robbery)
+print(plot_sexual_violation)
+print(plot_assault)
+```
+
 # References
+
+### should be added using BibTeX, reference R and any R pckgs you use, as well as the dataset.
 

### 2024-01-22 Toronto_Victims_of_Crimes/scripts/02-data_cleaning.R
Upload the cleaned_data

@@ -10,5 +10,9 @@ crime_data <- read.csv("Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv"
 filtered_data <- crime_data %>%
   filter(SEX %in% c("M", "F") & AGE_GROUP != "Unknown" & SUBTYPE != "Other")
 
+# Write cleaned_CSV file
+write_csv(
+  x = filtered_data,
+  file = "Toronto_Victims_of_Crimes/inputs/data/cleaned_data.csv"
+)
 head(filtered_data)
-

### 2024-01-22 Toronto_Victims_of_Crimes/scripts/02-data_cleaning.R
Rename filtered_data to cleaned_data

@@ -7,12 +7,12 @@ library(tidyverse)
 crime_data <- read.csv("Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv")
 
 # Filter out unknown values for SEX and rows with 'other' values for SUBTYPE
-filtered_data <- crime_data %>%
+cleaned_data <- crime_data %>%
   filter(SEX %in% c("M", "F") & AGE_GROUP != "Unknown" & SUBTYPE != "Other")
 
-# Write cleaned_CSV file
+# Write and download cleaned_CSV file
 write_csv(
-  x = filtered_data,
+  x = cleaned_data,
   file = "Toronto_Victims_of_Crimes/inputs/data/cleaned_data.csv"
 )
-head(filtered_data)
+head(cleaned_data)

### 2024-01-22 Toronto_Victims_of_Crimes/scripts/02-data_cleaning.R
Rename crime_data to unedited_data for the coherency on 02-data_cleaning.R file

@@ -4,10 +4,10 @@ library(lubridate)
 library(tidyverse)
 
 # Read the CSV file
-crime_data <- read.csv("Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv")
+unedited_data <- read.csv("Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv")
 
 # Filter out unknown values for SEX and rows with 'other' values for SUBTYPE
-cleaned_data <- crime_data %>%
+cleaned_data <- unedited_data %>%
   filter(SEX %in% c("M", "F") & AGE_GROUP != "Unknown" & SUBTYPE != "Other")
 
 # Write and download cleaned_CSV file

### 2024-01-22 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Update paper.qmd in the mid way

--- 2024-01-21 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
@@
 
+```{r}
+#### Preamble ####
+# Purpose: Read in data from the Toronto Police Annual Report - Victims of Crimes and provide relevant tables and graphs of the dataset.
+# Author: Chay Park
+# Email: chay.park@mail.utoronto.ca
+# Date: Jan 22, 2024
+# Prerequisites: Need to know where to get Toronto Police Annual Report - Victims of Crimes
+```
+
 # Abstract
+
+### top-level finding, what is the one thing that we learn about the world because of this paper?
+
+Often we see crimes on the global news and majority is happening in the States.
+Canada is known to be relatively safe country around the world.
+Toronto is one of the biggest city in Canada and thus the most populated.
+By investigating the dataset from Toronto Police Services, this report demonstrate the top three crimes reported over the year from 2014 to 2022.
 
@@
 
+Why I deal with this data?
+General trends of victims reporting following crimes, robbery, assault, sexual violation.
+Tables and graphs support visualize the trends over the year.
+From the dataset, we want to find out whether there are any point outlining from the trend between sexes, age_group, year.
+Then draw a correlation between other factor such as global pandemic.
+
+Impact of pandemic on reporting crimes,
+
+This paper use R to analyze a dataset from opendatatoronto.
+This dataset includes all identified victims of crimes against the person, including, but not limited to, those that may have been deemed unfounded after investigation, those that may have occurred outside the City of Toronto limits, or have no verified location.
+The paper extract age group, count, sex, subtype of crimes, report year.
+
+Visualize trend among the sex, age group per crime. The tendency of male not reporting might skew the result.
+
 # Data
 
+The unknown values for age_group, age_cohort, sex are excluded as they do not contribute to define data groups explicitly.
+The data set does not offer explicit details about the unknown values.
+Similarly, the other crime is not included in the cleaned_data set due to its uncertainty.
+Thus, the cleaned_data only serve top three reported crimes; robbery, assault, and sexual violation.
+Moreover, the sex is divided into two, female and male.
+Age group has three subgroups, adult, youth, child.
+
+```{r}
+# Install the necessary packages if not already installed
+# install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse"))
+
+# Load required libraries
+library(dplyr)
+library(knitr)
+library(lubridate)
+library(tidyverse)
+
+# Filter out unknown values for SEX and rows with 'other' values for SUBTYPE
+cleaned_data <- unedited_data %>%
+  filter(SEX %in% c("M", "F") & AGE_GROUP != "Unknown" & SUBTYPE != "Other")
+
+head(cleaned_data)
+```
+
+The table below showcases the general trend on the number of victims in different age group.
+Age information is based on the year that crime was reported.
+Adult is considered the group at an age of 18 or older.
+The age of the youth group is between 12 to 17.
+Below 12 is considered the child group.
+
+```{r}
+#### Table 1a ####
+# Count the Child group victims, Youth group victims, Adult group victims over the year from 2014 to 2022
+####  ####
+
+# Load required libraries
+library(dplyr)
+library(knitr)
+library(lubridate)
+library(tidyverse)
+
+# Filter rows with Adult, Child, and Youth in AGE_GROUP
+filtered_data <- cleaned_data %>%
+  filter(AGE_GROUP %in% c("Adult", "Child", "Youth"))
+
+# Create a new column for Age Cohort based on Age Group
+filtered_data <- filtered_data %>%
+  mutate(Age_Cohort = case_when(
+    AGE_GROUP == "Child" ~ "Child",
+    AGE_GROUP == "Adult" ~ "Adult",
+    AGE_GROUP == "Youth" ~ "Youth",
+    TRUE ~ "Other"  # Include an "Other" category for any unexpected values
+  ))
+
+# Filter data for the years 2014 to 2022
+filtered_data <- filtered_data %>%
+  filter(REPORT_YEAR >= 2014 & REPORT_YEAR <= 2022)
+
+# Create a table counting the number of victims for each Age Cohort over the years
+age_cohort_table <- filtered_data %>%
+  group_by(REPORT_YEAR, Age_Cohort) %>%
+  summarise(Victims_Count = sum(COUNT_))
+
+# Pivot the data to have Adult, Youth, Child as columns in that order
+pivoted_table <- age_cohort_table %>%
+  pivot_wider(names_from = Age_Cohort, values_from = Victims_Count, values_fill = 0, 
+              values_fn = list(Victims_Count = sum)) %>%
+  select(REPORT_YEAR, Adult, Youth, Child)
+
+# Print the table using knitr
+kable(pivoted_table, format = "markdown", caption = "Total number of victims in different age group from 2014 to 2022")
+
+```
+
+Table 1a counts the total number of victims for each age group over the years.
+It is obvious to find out that Adult victim group is reported the most and the Child victim group is reported the least.
+Also, it is noticeable that in 2020, the reported number of victims are far less than the other years.
+In three different age group, crime reporting rate significantly reduced by the impact of COVID and its lockdown.
+
+```{r}
+#### Bar graph 1a ####
+# Bar graph 1a illustrates the number of reported crimes in different age group over the year from 2014 to 2022. 
+#### ####
+
+# Load required libraries
+library(dplyr)
+library(ggplot2)
+
+# Refer to the pivoted table from table 1a
+
+# Create bar graphs for each age group
+bar_plot <- ggplot(pivoted_table, aes(x = REPORT_YEAR)) +
+  geom_bar(aes(y = Adult, fill = "Adult"), stat = "identity", position = "stack") +
+  geom_bar(aes(y = Youth, fill = "Youth"), stat = "identity", position = "stack") +
+  geom_bar(aes(y = Child, fill = "Child"), stat = "identity", position = "stack") +
+  labs(title = "Number of Reported Crimes in Different Age Group Over the Years",
+       x = "Year",
+       y = "Number of reported crimes") +
+  scale_fill_manual(values = c(Adult = "blue", Youth = "green", Child = "orange"),
+                    name = "Age Group") +
+  theme_minimal() +
+  scale_x_continuous(breaks = seq(2014, 2022, by = 1))
+
+# Print the bar plot
+print(bar_plot)
+
+```
+
+Bar graph 1a refers table 1a.
+By visualizing the age group into a bar per year, it is clear to see that majority of victims of reported crimes are adult.
+Also, the bars are showing ascending order from the year 2014 to 2018 but the reported crimes significantly drop between 2019 and 2020.
+One possible reason is because of COVID.
+
+```{r}
+# Load required libraries
+library(dplyr)
+library(knitr)
+library(lubridate)
+library(tidyverse)
+
+# Filter data for the years 2014 to 2022
+filtered_data <- cleaned_data %>%
+  filter(REPORT_YEAR >= 2014 & REPORT_YEAR <= 2022)
+
+# Create a table counting the number of victims for each crime subtype over the years
+crime_subtype_table <- filtered_data %>%
+  group_by(REPORT_YEAR, SUBTYPE) %>%
+  summarise(Victims_Count = sum(COUNT_))
+
+# Pivot the data to have Assault, Sexual Violation, Robbery as columns
+pivoted_table <- crime_subtype_table %>%
+  pivot_wider(names_from = SUBTYPE, values_from = Victims_Count, values_fill = 0)
+
+# Print the table using knitr
+kable(pivoted_table, format = "markdown", caption = "Table for Victims Count by Crime Subtype Over the Years")
+
+```
+
+```{r}
+# Load required libraries
+library(dplyr)
+library(ggplot2)
+
+# Assuming 'pivoted_table' is the table with Assault, Sexual Violation, Robbery columns from the above table code
+
+# Create bar graphs for each crime subtype
+bar_plot <- ggplot(pivoted_table, aes(x = REPORT_YEAR)) +
+  geom_bar(aes(y = Assault, fill = "Assault"), stat = "identity", position = "stack") +
+  geom_bar(aes(y = Sexual_Violation, fill = "Sexual Violation"), stat = "identity", position = "stack") +
+  geom_bar(aes(y = Robbery, fill = "Robbery"), stat = "identity", position = "stack") +
+  labs(title = "Victims Count by Crime Subtype Over the Years",
+       x = "Year",
+       y = "Count") +
+  scale_fill_manual(values = c("Assault" = "grey", "Sexual Violation" = "brown", "Robbery" = "pink"),
+                    name = "Crime Subtype") +
+  theme_minimal() +
+  scale_x_continuous(breaks = seq(2014, 2022, by = 1))
+
+# Print the bar plot
+print(bar_plot)
+```
+
 # References
+
+### should be added using BibTeX, reference R and any R pckgs you use, as well as the dataset.
 

### 2024-01-22 Toronto_Victims_of_Crimes/scripts/01-download_data.R
Rewrite install package code

@@ -10,10 +10,7 @@
 #### Save data ####
 
 # Install the package
-install.packages("opendatatoronto")
-install.packages("knitr")
-install.packages("lubridate")
-install.packages("tidyverse")
+# install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse"))
 
 # See a list of available packages
 library(knitr)

### 2024-01-22 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Edit codes for data analysis

@@
   geom_bar(aes(y = Child, fill = "Child"), stat = "identity", position = "stack") +
-  labs(title = "Number of Reported Crimes in Different Age Group Over the Years",
+  labs(title = "Number of Reported Victims of Crimes in Different Age Group Over the Years",
        x = "Year",
@@
 # Pivot the data to have Assault, Sexual Violation, Robbery as columns
-pivoted_table <- crime_subtype_table %>%
+pivoted_table2 <- crime_subtype_table %>%
   pivot_wider(names_from = SUBTYPE, values_from = Victims_Count, values_fill = 0)
@@
 # Print the table using knitr
-kable(pivoted_table, format = "markdown", caption = "Table for Victims Count by Crime Subtype Over the Years")
+kable(pivoted_table2, format = "markdown", caption = "Table for Victims Count by Crime Subtype Over the Years")
 
@@
 
-# Assuming 'pivoted_table' is the table with Assault, Sexual Violation, Robbery columns from the above table code
+# Assuming 'pivoted_table2' is the table with Assault, Sexual Violation, Robbery columns from the above table code
 
 # Create bar graphs for each crime subtype
-bar_plot <- ggplot(pivoted_table, aes(x = REPORT_YEAR)) +
+bar_plot <- ggplot(pivoted_table2, aes(x = REPORT_YEAR)) +
   geom_bar(aes(y = Assault, fill = "Assault"), stat = "identity", position = "stack") +
-  geom_bar(aes(y = Sexual_Violation, fill = "Sexual Violation"), stat = "identity", position = "stack") +
+  geom_bar(aes(y = `Sexual Violation`, fill = "Sexual Violation"), stat = "identity", position = "stack") +
   geom_bar(aes(y = Robbery, fill = "Robbery"), stat = "identity", position = "stack") +
@@
        x = "Year",
-       y = "Count") +
+       y = "Number of Reported Victims of Crimes") +
   scale_fill_manual(values = c("Assault" = "grey", "Sexual Violation" = "brown", "Robbery" = "pink"),
@@
   scale_x_continuous(breaks = seq(2014, 2022, by = 1))
+
+# Print the bar plot
+print(bar_plot)
+
+```
+
+```{r}
+# Load required libraries
+library(dplyr)
+library(ggplot2)
+
+# Assuming 'crime_counts' is the data frame with relevant columns
+
+# Filter the data for Sexual Violation
+sexual_violation_data <- cleaned_data %>%
+  filter(SUBTYPE == "Sexual Violation")
+
+# Create a bar graph for Sexual Violation with groups for AGE_GROUP
+bar_plot <- ggplot(sexual_violation_data, aes(x = REPORT_YEAR, y = COUNT_, fill = AGE_GROUP)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  labs(title = "Victims Count of Sexual Violation by Age Group Over the Years",
+       x = "Year",
+       y = "Number of Reported Victims of Sexual Violation",
+       fill = "Age Group") +
+  theme_minimal() +
+  scale_x_continuous(breaks = seq(min(sexual_violation_data$REPORT_YEAR), max(sexual_violation_data$REPORT_YEAR), by = 1)) +
+  scale_fill_manual(values = c("Child" = "yellow", "Youth" = "orange", "Adult" = "skyblue"))
 

### 2024-01-22 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Update paper.qmd file

@@
 library(tidyverse)
+
+# Read CSV
+unedited_data <- read.csv("Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv")
 
@@
 One possible reason is because of COVID.
+Correlation between COVID pandemic and report crime rates 논문 찾아서 첨부
+
+```{r}
+# Load required libraries
+library(dplyr)
+library(ggplot2)
+
+# Filter the data for Sexual Violation
+sexual_violation_data <- cleaned_data %>%
+  filter(SUBTYPE == "Sexual Violation")
+
+# Create a bar graph for Sexual Violation with groups for AGE_GROUP
+bar_plot <- ggplot(sexual_violation_data, aes(x = REPORT_YEAR, y = COUNT_, fill = AGE_GROUP)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  labs(title = "Victims Count of Sexual Violation by Age Group Over the Years",
+       x = "Year",
+       y = "Number of Reported Victims of Sexual Violation",
+       fill = "Age Group") +
+  theme_minimal() +
+  scale_x_continuous(breaks = seq(min(sexual_violation_data$REPORT_YEAR), max(sexual_violation_data$REPORT_YEAR), by = 1)) +
+  scale_fill_manual(values = c("Child" = "yellow", "Youth" = "orange", "Adult" = "skyblue"))
+
+# Print the bar plot
+print(bar_plot)
+```
+
+From 2014 to 2020, the trend shows that the adult group is twice the size of the child group.
+Up until 2020, victims of sexual violation was predominantly adult age group.
+However, as of 2021, the youth victim group surpass the amount of the adult victim group.
+무슨 사건이 일어났을까?
+왜 youth group이 더 높아졌는지 사유 찾기
+
+```{r}
+# Load required libraries
+library(dplyr)
+library(ggplot2)
+
+# Filter the data for Assault
+assault_data <- cleaned_data %>%
+  filter(SUBTYPE == "Assault")
+
+# Create a bar graph for Assault with groups for AGE_GROUP
+bar_plot <- ggplot(assault_data, aes(x = REPORT_YEAR, y = COUNT_, fill = AGE_GROUP)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  labs(title = "Victims Count of Assault by Age Group Over the Years",
+       x = "Year",
+       y = "Number of Reported Victims of Assault",
+       fill = "Age Group") +
+  theme_minimal() +
+  scale_x_continuous(breaks = seq(min(assault_data$REPORT_YEAR), max(assault_data$REPORT_YEAR), by = 1)) +
+  scale_fill_manual(values = c("Child" = "yellow", "Youth" = "orange", "Adult" = "skyblue"))
+
+# Print the bar plot
+print(bar_plot)
+```
+
+The graph illustrates the ascending trend in number of victims of assault in city of Toronto over the year from 2014 to 2022.
+COVID does not seem to be a factor that skews the trend.
+Though, size of both child and youth victim groups got halved.
+Compared to child victim group, size of youth victim group grows fast.
+
+```{r}
+# Load required libraries
+library(dplyr)
+library(ggplot2)
+
+# Filter the data for Robbery
+robbery_data <- cleaned_data %>%
+  filter(SUBTYPE == "Robbery")
+
+# Create a bar graph for Robbery with groups for AGE_GROUP
+bar_plot <- ggplot(robbery_data, aes(x = REPORT_YEAR, y = COUNT_, fill = AGE_GROUP)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  labs(title = "Victims Count of Robbery by Age Group Over the Years",
+       x = "Year",
+       y = "Number of Reported Victims of Robbery",
+       fill = "Age Group") +
+  theme_minimal() +
+  scale_x_continuous(breaks = seq(min(robbery_data$REPORT_YEAR), max(robbery_data$REPORT_YEAR), by = 1)) +
+  scale_fill_manual(values = c("Child" = "yellow", "Youth" = "orange", "Adult" = "skyblue"))
+
+# Print the bar plot
+print(bar_plot)
+```
+
+As of 2018, youth group of victims of robbery diminished and it keeps at the lower level.
+COVID pandemic is the factor of bar graphs on the number of victim of robbery in different age group over the year.
+In 2020, victims of robbery in every age group significantly decreased.
+We could assume that lockdown mandate affect the decrease in victims.
 
@@
 
-```{r}
-# Load required libraries
-library(dplyr)
-library(ggplot2)
-
-# Assuming 'crime_counts' is the data frame with relevant columns
-
-# Filter the data for Sexual Violation
-sexual_violation_data <- cleaned_data %>%
-  filter(SUBTYPE == "Sexual Violation")
-
-# Create a bar graph for Sexual Violation with groups for AGE_GROUP
-bar_plot <- ggplot(sexual_violation_data, aes(x = REPORT_YEAR, y = COUNT_, fill = AGE_GROUP)) +
-  geom_bar(stat = "identity", position = "dodge") +
-  labs(title = "Victims Count of Sexual Violation by Age Group Over the Years",
-       x = "Year",
-       y = "Number of Reported Victims of Sexual Violation",
-       fill = "Age Group") +
-  theme_minimal() +
-  scale_x_continuous(breaks = seq(min(sexual_violation_data$REPORT_YEAR), max(sexual_violation_data$REPORT_YEAR), by = 1)) +
-  scale_fill_manual(values = c("Child" = "yellow", "Youth" = "orange", "Adult" = "skyblue"))
-
-# Print the bar plot
-print(bar_plot)
-```
-
 # References

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Update paper.qmd file and rendered it.

@@
 
-# Read CSV
-unedited_data <- read.csv("Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv")
+# list files
+list.files(path = "Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv")
+unedited_data <- list.files(path = "Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv")
 
@@
 
-### should be added using BibTeX, reference R and any R pckgs you use, as well as the dataset.
+### should be added using BibTeX,
 

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Update the paper.qmd file

--- 2024-01-22 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
@@
 author: "Chay Park"
-date: 22 January 2024
+date: today
 format: pdf
 editor: visual
+bibliography: references.bib
 ---
@@
 ```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| include: false
+
 #### Preamble ####
@@
 
-```{r}
-# Install the necessary packages if not already installed
-# install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse"))
-
-# Load required libraries
-library(dplyr)
-library(knitr)
-library(lubridate)
-library(tidyverse)
-
-# Read CSV
-unedited_data <- read.csv("Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv")
-
-# Filter out unknown values for SEX and rows with 'other' values for SUBTYPE
-cleaned_data <- unedited_data %>%
-  filter(SEX %in% c("M", "F") & AGE_GROUP != "Unknown" & SUBTYPE != "Other")
-
-head(cleaned_data)
-```
-
 The table below showcases the general trend on the number of victims in different age group.
@@
 ```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
 #### Table 1a ####
@@
 ####  ####
+
+# Install the necessary packages if not already installed
+install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "flextable"))
 
@@
 library(tidyverse)
+library(flextable)
+
+# Load the csv file
+cleaned_data <- read_csv(file = here::here("Toronto_Victims_of_Crimes/inputs/data/cleaned_data.csv"))
 
@@
 
-# Print the table using knitr
-kable(pivoted_table, format = "markdown", caption = "Total number of victims in different age group from 2014 to 2022")
+# Print the table
+flextable(head(pivoted_table))
 
@@
 ```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
 #### Bar graph 1a ####
@@
 ```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
 # Load required libraries
@@
 library(ggplot2)
+
+# Load the csv file
+cleaned_data <- read_csv(file = here::here("Toronto_Victims_of_Crimes/inputs/data/cleaned_data.csv"))
 
@@
 
-# Print the table using knitr
-kable(pivoted_table2, format = "markdown", caption = "Table for Victims Count by Crime Subtype Over the Years")
+# Print the table
+flextable(head(pivoted_table2))
 
@@
 
-### should be added using BibTeX, reference R and any R pckgs you use, as well as the dataset.
-
-Gelfand, Sharla. 2020. *Opendatatoronto : Access the City of Toronto Open Data Portal*
-
-R Core Team. 2020. *R: A Language and Environment for Statistical Computing.* Vienna, Austria: R Foundation for Statistical Computing. https://www.R-project.org/.
-
-Toronto Police Services. 2023. *TPS Police Annual Statistical Report - Victims of Crimes*
-
-Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy D'Agostino McGowan, Romain François, Garrett Grolemund, et al.
-2019.
-"Welcome to the tidyverse." *Journal of Open Source Software* 4 (43): 1686.
-https://doi.org/10.21105/joss.01686.
-
-\
-Wickham, Hadley, Romain François, Lionel Henry, and Kirill Müller. 2021. *Dplyr: A Grammar of Data Manipulation.*https://CRAN.R-project.org/package=dplyr.
-
-Xie, Yihui.
-2014.
-"Knitr: A Comprehensive Tool for Reproducible Research in R." *In Implementing Reproducible Computational Research*, edited by Victoria Stodden, Friedrich Leisch, and Roger D.
-Peng.
-Chapman; Hall/CRC.
-http://www.crcpress.com/product/isbn/9781466561595.
+---
+nocite: '@*'
+---

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Update the file

@@
 
-The table below showcases the general trend on the number of victims in different age group.
+The table (@tbl-totalsum_table) below showcases the general trend on the number of victims in different age group.
 Age information is based on the year that crime was reported.
@@
 #| message: false
+#| label: tbl-totalsum-table
+#| tbl-cap: "Total sum of victims in different age group throughout the years"
 
@@
 # Install the necessary packages if not already installed
-install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "flextable"))
+# install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "flextable"))
 
@@
 
-Table 1a counts the total number of victims for each age group over the years.
+Table 1a (@tbl-totalsum-table) counts the total number of victims for each age group over the years.
 It is obvious to find out that Adult victim group is reported the most and the Child victim group is reported the least.
@@
 #| message: false
+#| label: tbl-totalsum-bar
+#| tbl-cap: "Number of Reported Victims of Crimes in Different Age Group Over the Years"
 
@@
   geom_bar(aes(y = Child, fill = "Child"), stat = "identity", position = "stack") +
-  labs(title = "Number of Reported Victims of Crimes in Different Age Group Over the Years",
-       x = "Year",
+  labs(x = "Year",
        y = "Number of reported crimes") +
@@
 
-Bar graph 1a refers table 1a.
+Bar graph (@tbl-totalsum-bar) refers table (@tbl-totalsum-table).
 By visualizing the age group into a bar per year, it is clear to see that majority of victims of reported crimes are adult.
@@
 #| message: false
+#| label: tbl-sv-bar
+#| tbl-cap: "Victims Count of Sexual Violation by Age Group Over the Years"
 
@@
   geom_bar(stat = "identity", position = "dodge") +
-  labs(title = "Victims Count of Sexual Violation by Age Group Over the Years",
-       x = "Year",
+  labs(x = "Year",
        y = "Number of Reported Victims of Sexual Violation",
@@
 #| message: false
+#| label: tbl-a-bar
+#| tbl-cap: "Victims Count of Assault by Age Group Over the Years"
 
@@
 
-The graph illustrates the ascending trend in number of victims of assault in city of Toronto over the year from 2014 to 2022.
+The graph (@tbl-a-bar) illustrates the ascending trend in number of victims of assault in city of Toronto over the year from 2014 to 2022.
 COVID does not seem to be a factor that skews the trend.
@@
 #| message: false
+#| label: tbl-r-bar
+#| tbl-cap: "Victims Count of Robbery by Age Group Over the Years"
 
@@
   geom_bar(stat = "identity", position = "dodge") +
-  labs(title = "Victims Count of Robbery by Age Group Over the Years",
-       x = "Year",
+  labs(x = "Year",
        y = "Number of Reported Victims of Robbery",
@@
 
-As of 2018, youth group of victims of robbery diminished and it keeps at the lower level.
+Graph (@tbl-r-bar) depicts that as of 2018, youth group of victims of robbery diminished and it keeps at the lower level.
 COVID pandemic is the factor of bar graphs on the number of victim of robbery in different age group over the year.
@@
 #| message: false
+#| label: tbl-crimetype-table
+#| tbl-cap: "Total number of victims counted for each crime from the year 2014 to 2022"
 
@@
 #| message: false
+#| label: tbl-crimesubtype-bar
+#| tbl-cap: "Victims Count by Crime Subtype Over the Years"
 
@@
   geom_bar(aes(y = Robbery, fill = "Robbery"), stat = "identity", position = "stack") +
-  labs(title = "Victims Count by Crime Subtype Over the Years",
-       x = "Year",
+  labs(x = "Year",
        y = "Number of Reported Victims of Crimes") +

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Update the cross-referencing and labels

@@
 
-### top-level finding, what is the one thing that we learn about the world because of this paper?
+### Top-level finding, what is the one thing that we learn about the world because of this paper?
 
@@
 
-The table (@tbl-totalsum_table) below showcases the general trend on the number of victims in different age group.
+The table (@tbl-totalsum-table) below showcases the general trend on the number of victims in different age group.
 Age information is based on the year that crime was reported.
@@
 # Install the necessary packages if not already installed
-# install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "flextable"))
+install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "kableExtra"))
 
@@
 library(tidyverse)
-library(flextable)
+library(kableExtra)
 
@@
 
-# Print the table
-flextable(head(pivoted_table))
+# Print the table with additional styling
+kable(pivoted_table, caption = "Count of Child, Youth, and Adult group victims over the years from 2014 to 2022", format = "html") %>%
+  kable_styling(full_width = FALSE) %>%
+  add_header_above(c(" ", "Victims Count" = 3))
 
@@
 #| message: false
-#| label: tbl-totalsum-bar
-#| tbl-cap: "Number of Reported Victims of Crimes in Different Age Group Over the Years"
+#| label: fig-totalsum-graph
+#| fig-cap: "Number of Reported Victims of Crimes in Different Age Group Over the Years"
 
@@
 
-Bar graph (@tbl-totalsum-bar) refers table (@tbl-totalsum-table).
+Bar graph (@fig-totalsum-graph) refers table (@tbl-totalsum-table).
 By visualizing the age group into a bar per year, it is clear to see that majority of victims of reported crimes are adult.
@@
 #| message: false
-#| label: tbl-sv-bar
-#| tbl-cap: "Victims Count of Sexual Violation by Age Group Over the Years"
+#| label: fig-sv-graph
+#| fig-cap: "Victims Count of Sexual Violation by Age Group Over the Years"
 
@@
 
-From 2014 to 2020, the trend shows that the adult group is twice the size of the child group.
+From 2014 to 2020 (@fig-sv-graph), the trend shows that the adult group is twice the size of the child group.
 Up until 2020, victims of sexual violation was predominantly adult age group.
@@
 #| message: false
-#| label: tbl-a-bar
-#| tbl-cap: "Victims Count of Assault by Age Group Over the Years"
+#| label: fig-a-graph
+#| fig-cap: "Victims Count of Assault by Age Group Over the Years"
 
@@
   geom_bar(stat = "identity", position = "dodge") +
-  labs(title = "Victims Count of Assault by Age Group Over the Years",
-       x = "Year",
+  labs(x = "Year",
        y = "Number of Reported Victims of Assault",
@@
 
-The graph (@tbl-a-bar) illustrates the ascending trend in number of victims of assault in city of Toronto over the year from 2014 to 2022.
+The graph (@fig-a-graph) illustrates the ascending trend in number of victims of assault in city of Toronto over the year from 2014 to 2022.
 COVID does not seem to be a factor that skews the trend.
@@
 #| message: false
-#| label: tbl-r-bar
-#| tbl-cap: "Victims Count of Robbery by Age Group Over the Years"
+#| label: fig-r-graph
+#| fig-cap: "Victims Count of Robbery by Age Group Over the Years"
 
@@
 
-Graph (@tbl-r-bar) depicts that as of 2018, youth group of victims of robbery diminished and it keeps at the lower level.
+Graph (@fig-r-graph) depicts that as of 2018, youth group of victims of robbery diminished and it keeps at the lower level.
 COVID pandemic is the factor of bar graphs on the number of victim of robbery in different age group over the year.
@@
 # Pivot the data to have Assault, Sexual Violation, Robbery as columns
-pivoted_table2 <- crime_subtype_table %>%
+pivoted_table <- crime_subtype_table %>%
   pivot_wider(names_from = SUBTYPE, values_from = Victims_Count, values_fill = 0)
 
-# Print the table
-flextable(head(pivoted_table2))
+# Print the table using kable with additional styling
+kable(pivoted_table, caption = "Total number of victims counted for each crime from the year 2014 to 2022", format = "html") %>%
+  kable_styling(full_width = FALSE) %>%
+  add_header_above(c(" ", "Victims Count" = 3))
 
@@
 #| message: false
-#| label: tbl-crimesubtype-bar
-#| tbl-cap: "Victims Count by Crime Subtype Over the Years"
+#| label: fig-subtype-graph
+#| fig-cap: "Victims Count by Crime Subtype Over the Years"
 

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
update paper-files

@@
 # Print the table using kable with additional styling
-kable(pivoted_table, caption = "Total number of victims counted for each crime from the year 2014 to 2022", format = "html") %>%
+kable(pivoted_table2, caption = "Total number of victims counted for each crime from the year 2014 to 2022", format = "html") %>%
   kable_styling(full_width = FALSE) %>%

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Add prefer-html: true to utilize a function to upgrade table visualization

--- 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
@@
 bibliography: references.bib
+prefer-html: true
 ---
@@
 
-### Top-level finding, what is the one thing that we learn about the world because of this paper?
+### top-level finding, what is the one thing that we learn about the world because of this paper?
 
@@
 # Pivot the data to have Assault, Sexual Violation, Robbery as columns
-pivoted_table <- crime_subtype_table %>%
+pivoted_table_2 <- crime_subtype_table %>%
   pivot_wider(names_from = SUBTYPE, values_from = Victims_Count, values_fill = 0)
@@
 # Print the table using kable with additional styling
-kable(pivoted_table, caption = "Total number of victims counted for each crime from the year 2014 to 2022", format = "html") %>%
+kable(pivoted_table_2, caption = "Total number of victims counted for each crime from the year 2014 to 2022", format = "html") %>%
   kable_styling(full_width = FALSE) %>%
@@
 
-# Assuming 'pivoted_table2' is the table with Assault, Sexual Violation, Robbery columns from the above table code
+# Assuming 'pivoted_table_2' is the table with Assault, Sexual Violation, Robbery columns from the above table code
 
 # Create bar graphs for each crime subtype
-bar_plot <- ggplot(pivoted_table2, aes(x = REPORT_YEAR)) +
+bar_plot <- ggplot(pivoted_table_2, aes(x = REPORT_YEAR)) +
   geom_bar(aes(y = Assault, fill = "Assault"), stat = "identity", position = "stack") +

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Update the color code

@@
        y = "Number of reported crimes") +
-  scale_fill_manual(values = c(Adult = "blue", Youth = "green", Child = "orange"),
+  scale_fill_manual(values = c(Adult = "skyblue", Youth = "orange", Child = "pink"),
                     name = "Age Group") +
@@
   scale_x_continuous(breaks = seq(min(sexual_violation_data$REPORT_YEAR), max(sexual_violation_data$REPORT_YEAR), by = 1)) +
-  scale_fill_manual(values = c("Child" = "yellow", "Youth" = "orange", "Adult" = "skyblue"))
+  scale_fill_manual(values = c("Child" = "pink", "Youth" = "orange", "Adult" = "skyblue"))
 
@@
   scale_x_continuous(breaks = seq(min(assault_data$REPORT_YEAR), max(assault_data$REPORT_YEAR), by = 1)) +
-  scale_fill_manual(values = c("Child" = "yellow", "Youth" = "orange", "Adult" = "skyblue"))
+  scale_fill_manual(values = c("Child" = "pink", "Youth" = "orange", "Adult" = "skyblue"))
 
@@
   scale_x_continuous(breaks = seq(min(robbery_data$REPORT_YEAR), max(robbery_data$REPORT_YEAR), by = 1)) +
-  scale_fill_manual(values = c("Child" = "yellow", "Youth" = "orange", "Adult" = "skyblue"))
+  scale_fill_manual(values = c("Child" = "pink", "Youth" = "orange", "Adult" = "skyblue"))
 
@@
 
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| label: fig-subtype-graph
-#| fig-cap: "Victims Count by Crime Subtype Over the Years"
-
-# Load required libraries
-library(dplyr)
-library(ggplot2)
-
-# Assuming 'pivoted_table_2' is the table with Assault, Sexual Violation, Robbery columns from the above table code
-
-# Create bar graphs for each crime subtype
-bar_plot <- ggplot(pivoted_table_2, aes(x = REPORT_YEAR)) +
-  geom_bar(aes(y = Assault, fill = "Assault"), stat = "identity", position = "stack") +
-  geom_bar(aes(y = `Sexual Violation`, fill = "Sexual Violation"), stat = "identity", position = "stack") +
-  geom_bar(aes(y = Robbery, fill = "Robbery"), stat = "identity", position = "stack") +
-  labs(x = "Year",
-       y = "Number of Reported Victims of Crimes") +
-  scale_fill_manual(values = c("Assault" = "grey", "Sexual Violation" = "brown", "Robbery" = "pink"),
-                    name = "Crime Subtype") +
-  theme_minimal() +
-  scale_x_continuous(breaks = seq(2014, 2022, by = 1))
-
-# Print the bar plot
-print(bar_plot)
-
-```
-
 # References

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Update on paper.qmd file

@@
 ---
-title: "paper"
+title: "Decoding Toronto's Crime Patterns: A Comprehensive Analysis of Victims and Trends (2014-2022)"
 author: "Chay Park"
-date: today
+date: 'January 23, 2024'
 format: pdf
@@
 prefer-html: true
+toc: true
+toc-depth: 3
 ---
@@
 
-# Abstract
+## Abstract
 
-### top-level finding, what is the one thing that we learn about the world because of this paper?
+In the period from 2014 to 2022, including the global Novel Coronavirus pandemic in 2019, this paper scrutinizes the Toronto Police annual statistical report on victims of crimes.
+Analyzing this extensive dataset reveals a correlation between the pandemic and crime rates, emphasizing broader trends in the top three crimes across different age groups.
+The findings underscore the nuanced relationship between external events, law enforcement, and crime reporting, offering insights into the complex interplay between specific events and crime statistics.
+This research contributes to a comprehensive understanding of societal dynamics, highlighting the potential impact of the pandemic on both crime rates and the reporting of victims of crimes over the years.
 
-Often we see crimes on the global news and majority is happening in the States.
-Canada is known to be relatively safe country around the world.
-Toronto is one of the biggest city in Canada and thus the most populated.
-By investigating the dataset from Toronto Police Services, this report demonstrate the top three crimes reported over the year from 2014 to 2022.
+# 1 Introduction
 
-# Introduction
+Analyzing this dataset becomes imperative as it unravels a nuanced narrative beneath the overarching claim of declining crime rates in Canada, as reported by Statistics Canada.
+Contrary to the general trend, the Statista Research department asserts that the overall crime rate in Canada has consistently decreased since 2000, with the 2021 crime rate approximately 30 percent lower than its peak in 2003.
+Property crime aligns with this decline, dropping by 30.6 percent during the same period (Statista Research Department 2021).
+However, a surprising surge in violent crime rates in 2021 challenges this narrative, suggesting a potential consequence of crime rates rebounding after a decline during the pandemic.
+This analysis focuses on discerning general trends in victims reporting specific crimes---robbery, assault, and sexual violation---utilizing tables and graphs to visualize these trends from 2014 to 2022.
+The objective is to identify distinctive patterns within the trend, considering variations across age groups and different crime types.
+Additionally, an exploration of potential correlations with external factors, such as the global pandemic, will be conducted.
 
-Why I deal with this data?
-General trends of victims reporting following crimes, robbery, assault, sexual violation.
-Tables and graphs support visualize the trends over the year.
-From the dataset, we want to find out whether there are any point outlining from the trend between sexes, age_group, year.
-Then draw a correlation between other factor such as global pandemic.
+This paper employs R (R Core Team 2020) to analyze a dataset sourced from opendatatoronto (Gelfand 2020), encompassing all identified victims of crimes against persons.
+This inclusive dataset considers cases that may have been deemed unfounded post-investigation, incidents occurring beyond the City of Toronto limits, or those lacking verified locations.
+The analysis extracts key variables such as report_year, subtype, age_group, and count\_, excluding age_cohort, sex, category, and assault_subtype.
+Omitted are unknown values for age_group, age_cohort, and sex, as they don't contribute explicitly to defining data groups.
+The dataset lacks explicit details regarding these unknown values.
+Additionally, the analysis focuses solely on the top three reported crimes---robbery, assault, and sexual violation.
+The exclusion of 'other' crimes in the cleaned_data set is attributed to its inherent uncertainty.
+Notably, the data within this paper centers on trends related to these three crimes, with age groups classified into three subgroups: adult, youth, and child.
+The overarching trend indicates a resurgence in reported victims of crimes following a period of decline, 2020 - 2021.
 
-Impact of pandemic on reporting crimes,
+The paper begins with a comprehensive overview, presenting a table illustrating the total number of victims across various age groups over the specified period.
+This overview is complemented by corresponding graphs derived from the table.
+The subsequent section delves into bar graphs detailing the reported victims' numbers within distinct age groups, individually addressing sexual violation, assault, and robbery.
+Finally, a concise table is presented, offering a quantitative measure of the number of victims for each crime across the report years.
 
-This paper use R to analyze a dataset from opendatatoronto.
-This dataset includes all identified victims of crimes against the person, including, but not limited to, those that may have been deemed unfounded after investigation, those that may have occurred outside the City of Toronto limits, or have no verified location.
-The paper extract age group, count, sex, subtype of crimes, report year.
+# 2 Data
 
-Visualize trend among the sex, age group per crime. The tendency of male not reporting might skew the result.
+The dataset can be analyzed in R (R Core Team 2020) using various packages.
+Notable packages include ggplot2 (Wickham et al.
+2016) for creating graphical representations, kableExtra (Zhu et al.
+2021) for enhancing table aesthetics, and lubridate (Grolemund et al.
+2021) for handling date-related operations.
+Additionally, the Tidyverse framework (Wickham et al.
+2019) provides a cohesive suite of tools, while Dplyr (Wickham et al.
+2021) is specifically useful for data manipulation.
+Knitr (Xie 2014) plays a crucial role in generating dynamic reports.
+Leveraging these packages allows for comprehensive data analysis, aiding in the creation of informative tables and figures that contribute to unraveling the narrative of crime victims in Toronto.
 
-# Data
-
-The unknown values for age_group, age_cohort, sex are excluded as they do not contribute to define data groups explicitly.
-The data set does not offer explicit details about the unknown values.
-Similarly, the other crime is not included in the cleaned_data set due to its uncertainty.
-Thus, the cleaned_data only serve top three reported crimes; robbery, assault, and sexual violation.
-Moreover, the sex is divided into two, female and male.
-Age group has three subgroups, adult, youth, child.
-
-The table (@tbl-totalsum-table) below showcases the general trend on the number of victims in different age group.
-Age information is based on the year that crime was reported.
-Adult is considered the group at an age of 18 or older.
-The age of the youth group is between 12 to 17.
-Below 12 is considered the child group.
+The table (@tbl-totalsum-table) above illustrates the overarching trend in the number of victims across distinct age groups.
+The age categorization is determined by the reporting year, with the "Adult" group encompassing individuals aged 18 or older.
+The "Youth" group comprises individuals between the ages of 12 and 17, while those below 12 fall into the "Child" group.
+This presentation aims to provide a comprehensive overview of victim counts within these age cohorts over the years from 2014 to 2022.
 
@@
 
-Table 1a (@tbl-totalsum-table) counts the total number of victims for each age group over the years.
-It is obvious to find out that Adult victim group is reported the most and the Child victim group is reported the least.
-Also, it is noticeable that in 2020, the reported number of victims are far less than the other years.
-In three different age group, crime reporting rate significantly reduced by the impact of COVID and its lockdown.
+Table 1 (@tbl-totalsum-table) counts the total number of victims for each age group over the years.
+It is evident that the "Adult" victim group has consistently reported the highest number of incidents, while the "Child" victim group reports the least.
+Notably, the year 2020 stands out, revealing a substantial reduction in reported victim counts across all three age groups.
+This decline is attributed to the impact of COVID-19 and the ensuing lockdown measures, resulting in a significant reduction in crime reporting rates.
 
@@
 
-Bar graph (@fig-totalsum-graph) refers table (@tbl-totalsum-table).
-By visualizing the age group into a bar per year, it is clear to see that majority of victims of reported crimes are adult.
-Also, the bars are showing ascending order from the year 2014 to 2018 but the reported crimes significantly drop between 2019 and 2020.
-One possible reason is because of COVID.
-Correlation between COVID pandemic and report crime rates 논문 찾아서 첨부
+Graph 1 (@fig-totalsum-graph) corresponds to the information presented in table 1 (@tbl-totalsum-table).
+Visualizing the data by age group across each year reveals that the majority of reported crime victims fall into the "Adult" category.
+Notably, the bars exhibit an ascending trend from 2014 to 2018.
+However, a conspicuous drop in reported crimes is observed between 2019 and 2020.
+One plausible explanation for this decline is attributed to the impact of COVID-19, which significantly influenced crime reporting rates during this period.
 
@@
 
-From 2014 to 2020 (@fig-sv-graph), the trend shows that the adult group is twice the size of the child group.
-Up until 2020, victims of sexual violation was predominantly adult age group.
-However, as of 2021, the youth victim group surpass the amount of the adult victim group.
-무슨 사건이 일어났을까?
-왜 youth group이 더 높아졌는지 사유 찾기
-
 ```{r}
@@
 ```
-
-The graph (@fig-a-graph) illustrates the ascending trend in number of victims of assault in city of Toronto over the year from 2014 to 2022.
-COVID does not seem to be a factor that skews the trend.
-Though, size of both child and youth victim groups got halved.
-Compared to child victim group, size of youth victim group grows fast.
 
@@
 
-Graph (@fig-r-graph) depicts that as of 2018, youth group of victims of robbery diminished and it keeps at the lower level.
-COVID pandemic is the factor of bar graphs on the number of victim of robbery in different age group over the year.
-In 2020, victims of robbery in every age group significantly decreased.
-We could assume that lockdown mandate affect the decrease in victims.
+From 2014 to 2020, graph 2 (@fig-sv-graph), the trend indicates that the adult group is consistently twice the size of the child group.
+Up until 2020, victims of sexual violation were predominantly from the adult age group.
+However, as of 2021, the youth victim group has surpassed the number of adult victims.
+
+Graph 3 (@fig-a-graph) illustrates an ascending trend in the number of assault victims in the city of Toronto from 2014 to 2022.
+COVID does not appear to be a factor influencing the trend, although the sizes of both child and youth victim groups have decreased.
+The youth victim group has experienced a faster growth compared to the child victim group.
+
+Graph 4 (@fig-r-graph) depicts that as of 2018, the youth group of robbery victims diminished and has remained at a lower level.
+The COVID pandemic is a significant factor influencing the bar graphs depicting the number of robbery victims in different age groups over the years.
+In 2020, victims of robbery in every age group significantly decreased, indicating a possible impact of lockdown mandates on the decrease in victims.
+
+The analysis reveals notable trends in victims of crimes in Toronto from 2014 to 2022.
+While the overall pattern suggests a decline in reported crimes, the impact of the COVID-19 pandemic is evident in specific crime subtypes and age groups.
+Sexual violation cases, for instance, witnessed a shift in the dominant age group from adults to youth in 2021.
+Assault incidents displayed a consistent upward trend, unaffected by the pandemic, but with a reduction in the sizes of child and youth victim groups.
+In contrast, the number of robbery victims, particularly in the youth group, significantly decreased in 2020, likely influenced by pandemic-related lockdown measures.
+These findings provide valuable insights into the complex dynamics of crime reporting and its interaction with external events.
 
@@
 
-# References
+The onset of the COVID-19 pandemic in late 2019 introduced a significant factor that impacted crime trends throughout the subsequent years, especially in 2020 and extending up to 2022.
+One plausible explanation is the reduction in physical interactions among individuals, potentially leading to a decline in contact-based offenses such as sexual violence and robbery.
+However, it is crucial not to overlook the possibility of an increase in domestic violence during this period.
+Domestic settings may contribute to instances of sexual violence, presenting a contrasting outcome.
+
+# Reference
 

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Update the paper.qmd file

@@
 author: "Chay Park"
-date: 'January 23, 2024'
+date: today
+date-format: long
 format: pdf
@@
 ---
+
+∗Code and data supporting this analysis is available at:
+
+<https://github.com/Chay-HyunminPark/Toronto_CrimeVictims.git>[^1].
+
+[^1]: View the repository on GitHub.
+
+...
 
@@
 #| label: tbl-totalsum-table
-#| tbl-cap: "Total sum of victims in different age group throughout the years"
+#| tbl-cap: "Total Sum of Victims in Different Age Groups Throughout the Years"
 
@@
 # Install the necessary packages if not already installed
-install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "kableExtra"))
+# install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "kableExtra"))
 
@@
 #| label: fig-totalsum-graph
-#| fig-cap: "Number of Reported Victims of Crimes in Different Age Group Over the Years"
+#| fig-cap: "Number of Reported Victims of Crimes in Different Age Groups Over the Years"
 
@@
   labs(x = "Year",
-       y = "Number of reported crimes") +
+       y = "Number of Reported Victims of Crimes") +
   scale_fill_manual(values = c(Adult = "skyblue", Youth = "orange", Child = "pink"),
@@
 print(bar_plot)
-
 ```
@@
 #| label: tbl-crimetype-table
-#| tbl-cap: "Total number of victims counted for each crime from the year 2014 to 2022"
+#| tbl-cap: "Total Number of Victims Counted for Each Crime from the Year 2014 to 2022"
 
@@
   add_header_above(c(" ", "Victims Count" = 3))
-
 ```

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
final update paper files

@@
 This paper employs R (R Core Team 2020) to analyze a dataset sourced from opendatatoronto (Gelfand 2020), encompassing all identified victims of crimes against persons.
+The dataset under analysis comprises observations on the number of victims reported each year for crimes, including robbery, assault, and sexual violation, to the Toronto Police from 2014 to 2022.
 This inclusive dataset considers cases that may have been deemed unfounded post-investigation, incidents occurring beyond the City of Toronto limits, or those lacking verified locations.
@@
 # Install the necessary packages if not already installed
-# install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "kableExtra"))
+install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "kableExtra"))
 
@@
 
-# Reference
+# References
 

### 2024-01-24 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Rearrange the paper

@@
 date-format: long
+bibliography: references.bib
+abstract: In the period from 2014 to 2022, including the global Novel Coronavirus pandemic in 2019, this paper scrutinizes the Toronto Police annual statistical report on victims of crimes.
+Analyzing this extensive dataset reveals a correlation between the pandemic and crime rates, emphasizing broader trends in the top three crimes across different age groups.
+The findings underscore the nuanced relationship between external events, law enforcement, and crime reporting, offering insights into the complex interplay between specific events and crime statistics.
+This research contributes to a comprehensive understanding of societal dynamics, highlighting the potential impact of the pandemic on both crime rates and the reporting of victims of crimes over the years.
 format: pdf
 editor: visual
-bibliography: references.bib
 prefer-html: true
@@
 toc-depth: 3
+toc-title: Contents
+number-sections: true
+number-depth: 3
 ---
@@
 
-## Abstract
-
-In the period from 2014 to 2022, including the global Novel Coronavirus pandemic in 2019, this paper scrutinizes the Toronto Police annual statistical report on victims of crimes.
-Analyzing this extensive dataset reveals a correlation between the pandemic and crime rates, emphasizing broader trends in the top three crimes across different age groups.
-The findings underscore the nuanced relationship between external events, law enforcement, and crime reporting, offering insights into the complex interplay between specific events and crime statistics.
-This research contributes to a comprehensive understanding of societal dynamics, highlighting the potential impact of the pandemic on both crime rates and the reporting of victims of crimes over the years.
-
-# 1 Introduction
+# Introduction
 
@@
 
-# 2 Data
+# Data
 
@@
 
+\newpage
 ```{r}
@@
 ```
-
 Graph 1 (@fig-totalsum-graph) corresponds to the information presented in table 1 (@tbl-totalsum-table).
@@
 One plausible explanation for this decline is attributed to the impact of COVID-19, which significantly influenced crime reporting rates during this period.
+
+From 2014 to 2020, graph 2 (@fig-sv-graph), the trend indicates that the adult group is consistently twice the size of the child group.
+Up until 2020, victims of sexual violation were predominantly from the adult age group.
+However, as of 2021, the youth victim group has surpassed the number of adult victims.
 
@@
 
+Graph 3 (@fig-a-graph) illustrates an ascending trend in the number of assault victims in the city of Toronto from 2014 to 2022.
+COVID does not appear to be a factor influencing the trend, although the sizes of both child and youth victim groups have decreased.
+The youth victim group has experienced a faster growth compared to the child victim group.
+
 ```{r}
@@
 
-From 2014 to 2020, graph 2 (@fig-sv-graph), the trend indicates that the adult group is consistently twice the size of the child group.
-Up until 2020, victims of sexual violation were predominantly from the adult age group.
-However, as of 2021, the youth victim group has surpassed the number of adult victims.
-
-Graph 3 (@fig-a-graph) illustrates an ascending trend in the number of assault victims in the city of Toronto from 2014 to 2022.
-COVID does not appear to be a factor influencing the trend, although the sizes of both child and youth victim groups have decreased.
-The youth victim group has experienced a faster growth compared to the child victim group.
+\newpage
 
@@
 These findings provide valuable insights into the complex dynamics of crime reporting and its interaction with external events.
+
+\newpage
 
@@
 
+\newpage
+
 # References

### 2024-01-24 scripts/01-download_data.R
Correct the working directory path

@@ -42,6 +42,6 @@ victims_statistics
 # Write CSV file
 write_csv(
   x = victims_statistics,
-  file = "Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv"
+  file = "inputs/data/unedited_data.csv"
 )
 head(victims_statistics)

### 2024-01-24 scripts/02-data_cleaning.R

@@ -4,7 +4,7 @@ library(lubridate)
 library(tidyverse)
 
 # Read the CSV file
-unedited_data <- read.csv("Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv")
+unedited_data <- read.csv("inputs/data/unedited_data.csv")
 
 # Filter out unknown values for SEX and rows with 'other' values for SUBTYPE
 cleaned_data <- unedited_data %>%
@@ -13,6 +13,6 @@ cleaned_data <- unedited_data %>%
 # Write and download cleaned_CSV file
 write_csv(
   x = cleaned_data,
-  file = "Toronto_Victims_of_Crimes/inputs/data/cleaned_data.csv"
+  file = "inputs/data/cleaned_data.csv"
 )
 head(cleaned_data)

### 2024-01-25 outputs/paper/paper.qmd
Correct the working directory path
Update

--- 2024-01-24 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
@@
 ---
-title: "Decoding Toronto's Crime Patterns: A Comprehensive Analysis of Victims and Trends (2014-2022)"
+title: "Decoding Toronto's Crime Patterns"
+subtitle: "A Comprehensive Analysis of Victims and Trends (2014-2022)"
 author: "Chay Park"
@@
 date-format: long
-bibliography: references.bib
-abstract: In the period from 2014 to 2022, including the global Novel Coronavirus pandemic in 2019, this paper scrutinizes the Toronto Police annual statistical report on victims of crimes.
+abstract: "In the period from 2014 to 2022, including the global Novel Coronavirus pandemic in 2019, this paper scrutinizes the Toronto Police annual statistical report on victims of crimes.
 Analyzing this extensive dataset reveals a correlation between the pandemic and crime rates, emphasizing broader trends in the top three crimes across different age groups.
 The findings underscore the nuanced relationship between external events, law enforcement, and crime reporting, offering insights into the complex interplay between specific events and crime statistics.
-This research contributes to a comprehensive understanding of societal dynamics, highlighting the potential impact of the pandemic on both crime rates and the reporting of victims of crimes over the years.
+This research contributes to a comprehensive understanding of societal dynamics, highlighting the potential impact of the pandemic on both crime rates and the reporting of victims of crimes over the years."
 format: pdf
@@
 toc-title: Contents
+thanks: "Code and data are available at: https://github.com/Chay-HyunminPark/Toronto_CrimeVictims."
 number-sections: true
 number-depth: 3
+bibliography: references.bib
 ---
-
-∗Code and data supporting this analysis is available at:
-
-<https://github.com/Chay-HyunminPark/Toronto_CrimeVictims.git>[^1].
-
-[^1]: View the repository on GitHub.
-
-...
 
@@
 
+# Set seed for reproducibility
+set.seed(123)
+
 # Load the csv file
-cleaned_data <- read_csv(file = here::here("Toronto_Victims_of_Crimes/inputs/data/cleaned_data.csv"))
+cleaned_data <- read_csv(file = here::here("inputs/data/cleaned_data.csv"))
 
@@
 # Load the csv file
-cleaned_data <- read_csv(file = here::here("Toronto_Victims_of_Crimes/inputs/data/cleaned_data.csv"))
+cleaned_data <- read_csv(file = here::here("inputs/data/cleaned_data.csv"))
 

### 2024-01-25 scripts/00-simulate_data.R

@@ -9,7 +9,6 @@
 # Date: 20 January 2024
 # Contact: chay.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites:
 
 #### Workspace setup ####
 

### 2024-01-25 scripts/02-data_cleaning.R

@@ -1,3 +1,15 @@
+#### Preamble ####
+# Purpose: In the provided code, I generated a code to clean the raw unedited data.
+
+# Author: Chay Park
+# Date: 20 January 2024
+# Contact: chay.park@mail.utoronto.ca
+# License: MIT
+
+# Install packages if not already installed
+install.packages(c("dplyr", "knitr", "lubridate", "tidyverse"))
+
+# Load library
 library(dplyr)
 library(knitr)
 library(lubridate)

### 2024-01-25 scripts/03-test_data.R
Add the test code

@@ -1,0 +1,50 @@
+#### Preamble ####
+# Purpose: Run some tests code on cleaned data
+# Author: Chay Park
+# Date: 23 Janurary 2024
+# Contact: chay.park@mail.utoronto.ca
+# License: MIT
+
+#### Workspace setup ####
+library(tidyverse)
+
+#### Test data ####
+
+# Install and load dplyr if not already installed
+if (!requireNamespace("dplyr", quietly = TRUE)) {
+  install.packages("dplyr")
+}
+library(dplyr)
+
+# Set seed for reproducibility
+set.seed(123)
+
+# Load cleaned data
+cleaned_data
+
+# Display the first few rows of the dataset
+head(cleaned_data)
+
+#### Test codes ####
+
+# Test 1: Total Count by Crime Type
+
+# Hypothesis: The total count of crimes for each subtype is greater than 0.
+
+test_1 <- all(aggregate(COUNT_ ~ SUBTYPE, cleaned_data, sum)$count > 0)
+print("Test 1 (Total Count by Crime Type > 0):", test_1)
+
+# Test 2: Check for Missing Values
+
+# Hypothesis: There are no missing values in the dataset.
+
+test_2 <- all(!is.na(cleaned_data))
+print("Test 2 (No Missing Values):", test_2)
+
+# Test 3: No Missing Combinations
+
+# Hypothesis: There are no missing combinations in the dataset, 
+# and the count for every combination is either present or set to 0.
+
+test_3 <- all(cleaned_data$COUNT_ >= 0)
+print("Test 3 (No Missing Combinations):", test_3)

### 2024-01-25 outputs/paper/paper.qmd
Update the formatting

@@
 format: pdf
-editor: visual
 prefer-html: true
@@
 
-# Data
+# Data {#sec-data}
 
@@
 
-The table (@tbl-totalsum-table) above illustrates the overarching trend in the number of victims across distinct age groups.
+## Results
+
+### Number of Victims by Age Group
+
+@tbl-totalsum-table above illustrates the overarching trend in the number of victims across distinct age groups.
 The age categorization is determined by the reporting year, with the "Adult" group encompassing individuals aged 18 or older.
@@
 
-Table 1 (@tbl-totalsum-table) counts the total number of victims for each age group over the years.
+@tbl-totalsum-table counts the total number of victims for each age group over the years.
 It is evident that the "Adult" victim group has consistently reported the highest number of incidents, while the "Child" victim group reports the least.
@@
 
-\newpage
 ```{r}
@@
 ```
-Graph 1 (@fig-totalsum-graph) corresponds to the information presented in table 1 (@tbl-totalsum-table).
+
+@fig-totalsum-graph corresponds to the information presented in @tbl-totalsum-table.
 Visualizing the data by age group across each year reveals that the majority of reported crime victims fall into the "Adult" category.
@@
 
-From 2014 to 2020, graph 2 (@fig-sv-graph), the trend indicates that the adult group is consistently twice the size of the child group.
+\newpage
+
+### Reporting Rate on Sexual Violation
+
+From 2014 to 2020, @fig-sv-graph, the trend indicates that the adult group is consistently twice the size of the child group.
 Up until 2020, victims of sexual violation were predominantly from the adult age group.
@@
 
+### Reporting Rate on Assault
+
+@fig-a-graph illustrates an ascending trend in the number of assault victims in the city of Toronto from 2014 to 2022.
+COVID does not appear to be a factor influencing the trend, although the sizes of both child and youth victim groups have decreased.
+The youth victim group has experienced a faster growth compared to the child victim group.
+
 ```{r}
@@
 
-Graph 3 (@fig-a-graph) illustrates an ascending trend in the number of assault victims in the city of Toronto from 2014 to 2022.
-COVID does not appear to be a factor influencing the trend, although the sizes of both child and youth victim groups have decreased.
-The youth victim group has experienced a faster growth compared to the child victim group.
+\newpage
+
+### Reporting Rate on Robbery
+
+@fig-r-graph depicts that as of 2018, the youth group of robbery victims diminished and has remained at a lower level.
+The COVID pandemic is a significant factor influencing the bar graphs depicting the number of robbery victims in different age groups over the years.
+In 2020, victims of robbery in every age group significantly decreased, indicating a possible impact of lockdown mandates on the decrease in victims.
 
@@
 
-Graph 4 (@fig-r-graph) depicts that as of 2018, the youth group of robbery victims diminished and has remained at a lower level.
-The COVID pandemic is a significant factor influencing the bar graphs depicting the number of robbery victims in different age groups over the years.
-In 2020, victims of robbery in every age group significantly decreased, indicating a possible impact of lockdown mandates on the decrease in victims.
-
-The analysis reveals notable trends in victims of crimes in Toronto from 2014 to 2022.
-While the overall pattern suggests a decline in reported crimes, the impact of the COVID-19 pandemic is evident in specific crime subtypes and age groups.
-Sexual violation cases, for instance, witnessed a shift in the dominant age group from adults to youth in 2021.
-Assault incidents displayed a consistent upward trend, unaffected by the pandemic, but with a reduction in the sizes of child and youth victim groups.
-In contrast, the number of robbery victims, particularly in the youth group, significantly decreased in 2020, likely influenced by pandemic-related lockdown measures.
-These findings provide valuable insights into the complex dynamics of crime reporting and its interaction with external events.
-
-\newpage
+### Number of Victims for each crime
 
@@
 
+# Analysis
+
+The analysis reveals notable trends in victims of crimes in Toronto from 2014 to 2022.
+While the overall pattern suggests a decline in reported crimes, the impact of the COVID-19 pandemic is evident in specific crime subtypes and age groups.
+Sexual violation cases, for instance, witnessed a shift in the dominant age group from adults to youth in 2021.
+Assault incidents displayed a consistent upward trend, unaffected by the pandemic, but with a reduction in the sizes of child and youth victim groups.
+In contrast, the number of robbery victims, particularly in the youth group, significantly decreased in 2020, likely influenced by pandemic-related lockdown measures.
+These findings provide valuable insights into the complex dynamics of crime reporting and its interaction with external events.
+
+\newpage
+
 # References

### 2024-01-25 outputs/paper/paper.qmd
Improve writing

@@
 abstract: "In the period from 2014 to 2022, including the global Novel Coronavirus pandemic in 2019, this paper scrutinizes the Toronto Police annual statistical report on victims of crimes.
-Analyzing this extensive dataset reveals a correlation between the pandemic and crime rates, emphasizing broader trends in the top three crimes across different age groups.
-The findings underscore the nuanced relationship between external events, law enforcement, and crime reporting, offering insights into the complex interplay between specific events and crime statistics.
-This research contributes to a comprehensive understanding of societal dynamics, highlighting the potential impact of the pandemic on both crime rates and the reporting of victims of crimes over the years."
+By analyzing trends in the top three crimes across different age groups, the paper conveys a message on a correlation between the pandemic and crime rates.
+This research contributes to an understanding of societal dynamics, highlighting the potential impact of the pandemic on both crime rates and the reporting of victims of crimes over the years."
 format: pdf
@@
 
-Analyzing this dataset becomes imperative as it unravels a nuanced narrative beneath the overarching claim of declining crime rates in Canada, as reported by Statistics Canada.
-Contrary to the general trend, the Statista Research department asserts that the overall crime rate in Canada has consistently decreased since 2000, with the 2021 crime rate approximately 30 percent lower than its peak in 2003.
-Property crime aligns with this decline, dropping by 30.6 percent during the same period (Statista Research Department 2021).
-However, a surprising surge in violent crime rates in 2021 challenges this narrative, suggesting a potential consequence of crime rates rebounding after a decline during the pandemic.
+According to U.S.
+News, Canada placed second in the overall ranking for the best countries in 2023.
+One of the highest-scoring categories, 'Quality of Life,' ranks third, and its attribute, 'Safe,' scored 93.2 out of 100 (Best Countries 2023).
+Indeed, the Statista Research Department asserts that the overall crime rate in Canada has consistently decreased since 2000, with the 2021 crime rate approximately 30 percent lower than its peak in 2003 (Statista Research Department 2021).
+However, a surge in violent crime rates in 2021 challenges this claim, suggesting a potential consequence of crime rates rebounding after a decline during the pandemic.
 This analysis focuses on discerning general trends in victims reporting specific crimes---robbery, assault, and sexual violation---utilizing tables and graphs to visualize these trends from 2014 to 2022.
@@
 This paper employs R (R Core Team 2020) to analyze a dataset sourced from opendatatoronto (Gelfand 2020), encompassing all identified victims of crimes against persons.
-The dataset under analysis comprises observations on the number of victims reported each year for crimes, including robbery, assault, and sexual violation, to the Toronto Police from 2014 to 2022.
-This inclusive dataset considers cases that may have been deemed unfounded post-investigation, incidents occurring beyond the City of Toronto limits, or those lacking verified locations.
-The analysis extracts key variables such as report_year, subtype, age_group, and count\_, excluding age_cohort, sex, category, and assault_subtype.
-Omitted are unknown values for age_group, age_cohort, and sex, as they don't contribute explicitly to defining data groups.
-The dataset lacks explicit details regarding these unknown values.
-Additionally, the analysis focuses solely on the top three reported crimes---robbery, assault, and sexual violation.
-The exclusion of 'other' crimes in the cleaned_data set is attributed to its inherent uncertainty.
-Notably, the data within this paper centers on trends related to these three crimes, with age groups classified into three subgroups: adult, youth, and child.
-The overarching trend indicates a resurgence in reported victims of crimes following a period of decline, 2020 - 2021.
+The dataset comprises observations on the number of victims reported each year to the Toronto Police from 2014 to 2022.
+This considers cases that may have been deemed unfounded post-investigation, incidents occurring beyond the City of Toronto limits, or those lacking verified locations (Toronto Police Services 2023).
+The analysis extracts variables such as report_year, subtype, age_group, and count\_, excluding age_cohort, sex, category, and assault_subtype.
+Omitted are unknown values for age_group, age_cohort, and sex, as they do not contribute explicitly to defining data groups.
+The dataset lacks details regarding these unknown values.
+Additionally, the analysis focuses on the top three reported crimes---robbery, assault, and sexual violation.
+The exclusion of 'other' crimes in the cleaned_data set is attributed to its uncertainty.
+The data within this paper center on trends related to these three crimes, with age groups classified into three subgroups: adult, youth, and child.
+The trend indicates a resurgence in reported victims of crimes following a period of decline, 2020-2021.
 
-The paper begins with a comprehensive overview, presenting a table illustrating the total number of victims across various age groups over the specified period.
-This overview is complemented by corresponding graphs derived from the table.
+The paper begins with a general overview of the dataset, presenting a table illustrating the total number of victims across various age groups over the specified period.
+This overview is complemented by corresponding graphs.
 The subsequent section delves into bar graphs detailing the reported victims' numbers within distinct age groups, individually addressing sexual violation, assault, and robbery.
-Finally, a concise table is presented, offering a quantitative measure of the number of victims for each crime across the report years.
+Finally, a table offers a quantitative measure of the number of victims for each crime across the report years.
 
@@
 
-@tbl-totalsum-table above illustrates the overarching trend in the number of victims across distinct age groups.
+@tbl-totalsum-table above illustrates the trend in the number of victims across distinct age groups.
 The age categorization is determined by the reporting year, with the "Adult" group encompassing individuals aged 18 or older.
@@
 It is evident that the "Adult" victim group has consistently reported the highest number of incidents, while the "Child" victim group reports the least.
-Notably, the year 2020 stands out, revealing a substantial reduction in reported victim counts across all three age groups.
-This decline is attributed to the impact of COVID-19 and the ensuing lockdown measures, resulting in a significant reduction in crime reporting rates.
+Notably, the year 2020 stands out, revealing a reduction in reported victim counts across all three age groups.
+This decline is attributed to the impact of COVID-19 and the ensuing lockdown measures, resulting in a seemingly decrease in crime reporting rates.
 
@@
 Visualizing the data by age group across each year reveals that the majority of reported crime victims fall into the "Adult" category.
-Notably, the bars exhibit an ascending trend from 2014 to 2018.
+The bars exhibit an ascending trend from 2014 to 2018.
 However, a conspicuous drop in reported crimes is observed between 2019 and 2020.
-One plausible explanation for this decline is attributed to the impact of COVID-19, which significantly influenced crime reporting rates during this period.
+One plausible explanation for this decline is attributed to the impact of COVID-19, which influenced crime reporting rates during this period.
 
@@
 ```
+
+\newpage
 
@@
 The COVID pandemic is a significant factor influencing the bar graphs depicting the number of robbery victims in different age groups over the years.
-In 2020, victims of robbery in every age group significantly decreased, indicating a possible impact of lockdown mandates on the decrease in victims.
+In 2020, victims of robbery in every age group decreased, indicating a possible impact of lockdown mandates on the decrease in victims.
 
@@
 
-The onset of the COVID-19 pandemic in late 2019 introduced a significant factor that impacted crime trends throughout the subsequent years, especially in 2020 and extending up to 2022.
-One plausible explanation is the reduction in physical interactions among individuals, potentially leading to a decline in contact-based offenses such as sexual violence and robbery.
+The onset of the COVID-19 pandemic in late 2019 introduced a noticeable factor that impacted crime trends throughout the subsequent years, especially in 2020 and extending up to 2022.
+One reasonable explanation is the reduction in physical interactions among individuals, potentially leading to a decline in contact-based offenses such as sexual violence and robbery.
 However, it is crucial not to overlook the possibility of an increase in domestic violence during this period.
@@
 
-\newpage
-
 # Analysis
 
-The analysis reveals notable trends in victims of crimes in Toronto from 2014 to 2022.
+The analysis reveals trends in victims of crimes in Toronto from 2014 to 2022.
 While the overall pattern suggests a decline in reported crimes, the impact of the COVID-19 pandemic is evident in specific crime subtypes and age groups.
@@
 In contrast, the number of robbery victims, particularly in the youth group, significantly decreased in 2020, likely influenced by pandemic-related lockdown measures.
-These findings provide valuable insights into the complex dynamics of crime reporting and its interaction with external events.
+The findings offer insights between external events and crime statistics.
 

### 2024-01-25 outputs/paper/paper.qmd
Final change

@@
 title: "Decoding Toronto's Crime Patterns"
-subtitle: "A Comprehensive Analysis of Victims and Trends (2014-2022)"
+subtitle: "An Analysis of Victims and Trends (2014-2022)"
 author: "Chay Park"
@@
 abstract: "In the period from 2014 to 2022, including the global Novel Coronavirus pandemic in 2019, this paper scrutinizes the Toronto Police annual statistical report on victims of crimes.
-By analyzing trends in the top three crimes across different age groups, the paper conveys a message on a correlation between the pandemic and crime rates.
+By analyzing trends in the top three crimes across different age groups, the paper conveys a message on the correlation between the pandemic and crime rates.
 This research contributes to an understanding of societal dynamics, highlighting the potential impact of the pandemic on both crime rates and the reporting of victims of crimes over the years."
@@
 
-From 2014 to 2020, @fig-sv-graph, the trend indicates that the adult group is consistently twice the size of the child group.
+From 2014 to 2020, the trend indicates that the adult group is consistently twice the size of the child group @fig-sv-graph.
 Up until 2020, victims of sexual violation were predominantly from the adult age group.
@@
 #| label: fig-sv-graph
-#| fig-cap: "Victims Count of Sexual Violation by Age Group Over the Years"
+#| fig-cap: "Victims Count of Sexual Violation by Age Group"
 
@@
 #| label: fig-a-graph
-#| fig-cap: "Victims Count of Assault by Age Group Over the Years"
+#| fig-cap: "Victims Count of Assault by Age Group"
 
@@
 
-@fig-r-graph depicts that as of 2018, the youth group of robbery victims diminished and has remained at a lower level.
-The COVID pandemic is a significant factor influencing the bar graphs depicting the number of robbery victims in different age groups over the years.
+@fig-r-graph depicts that as of 2018, the number of robbery victims in the youth group diminished and has remained at a lower level.
+The COVID-19 pandemic is a factor influencing the bar graphs depicting the number of robbery victims in different age groups over the years.
 In 2020, victims of robbery in every age group decreased, indicating a possible impact of lockdown mandates on the decrease in victims.
@@
 #| label: fig-r-graph
-#| fig-cap: "Victims Count of Robbery by Age Group Over the Years"
+#| fig-cap: "Victims Count of Robbery by Age Group"
 
@@
 In contrast, the number of robbery victims, particularly in the youth group, significantly decreased in 2020, likely influenced by pandemic-related lockdown measures.
-The findings offer insights between external events and crime statistics.
+The findings offer insights into the relationship between external events and crime statistics.
 
